### 2015-04-23 intro.tex
slight update in abstract/intro

In this paper, we present \whoop, a new automatic approach that (i) statically analyses the concurrent behavior of Linux device drivers written in the C language and (ii) exploits the results from the static analysis to accelerate bug-finding. \whoop is empowered by \emph{static pairwise lockset analysis}, a novel technique for automatically verifying the absence of data races in Linux drivers. The key idea behind our approach is that a driver can be proven free from data races by (i) deriving a sound \emph{sequential} model that \emph{over-approximates} the originally concurrent program, (ii) instrumenting it for lockset analysis and race checking, and (iii) asserting that all accesses to the same shared resource are protected by at least one common lock. The immediate benefit is that our approach not only avoids reasoning about thread interleavings, and thus has the potential to scale well, but also allows the reuse of existing successful sequential verification techniques.

@@

To summarize, our contributions are as follows:
\begin{itemize}
\item We present \whoop, a practical tool for analyzing the concurrent behavior of Linux drivers and accelerating a plugged-in precise bug-finder.
\item We discuss static pairwise lockset analysis,  a sound scalable technique for automatically verifying absence of data races in Linux drivers.
\item We show that we can achieve a sound partial-order reduction using our technique and significantly accelerate \corral, a state-of-the-art bug-finder.
\item We analyze \sizeOfBenchmarks Linux drivers to show that \whoop is efficient in finding data races.
\end{itemize}

>>>>

In this paper, we present \whoop, a new fully automatic approach that (i) statically analyses device drivers written in the C language for data races and (ii) exploits the race-related results from the static analysis to accelerate bug-finding. \whoop is empowered by \emph{static pairwise lockset analysis}, a novel technique for automatically verifying the absence of data races in device drivers. The key idea behind our approach is that a driver can be proven free from data races by (i) deriving a sound \emph{sequential} model that \emph{over-approximates} the originally concurrent program, (ii) instrumenting it for lockset analysis and race checking, and (iii) asserting that all accesses to the same shared resource are protected by at least one common lock. The immediate benefit is that our approach not only avoids reasoning about thread interleavings, and thus has the potential to scale well, but also allows the reuse of existing successful sequential verification techniques.

@@

\whoop currently supports only Linux drivers, but the approach is generic enough and thus we believe that it can be used to analyze drivers from other operating systems (e.g. Windows) as well as other concurrent programs with similar structure (e.g. filesystems).

To summarize, our contributions are as follows:
\begin{itemize}
\item We present \whoop, a new fully automatic approach for analyzing device drivers for data races and accelerating bug-finding.
\item We discuss static pairwise lockset analysis,  a sound and scalable technique for automatically verifying the absence of data races in device drivers.
\item We show that we can achieve a sound partial-order reduction using our technique and significantly accelerate \corral, a state-of-the-art bug-finder.
\item We analyze \sizeOfBenchmarks Linux drivers to show that \whoop is efficient in finding data races.
\end{itemize}
